FoRTE baseline

### 2019-07-11 analysis/paper/paper.Rmd
Minor tweaks to RTM notes

$$ ext_1 = \phi_1 \TAI_l $$
$$ ext_2 = \phi_2 \TAI_l $$
$$ \tau_{diff} = (1 - CAI) - CAI exp\left( -ext_1 - ext_2 \right) ext_1^2 e^{exp_1} E_i(-exp_1) + (ext_1 - 1)$$

@@

Backscatter for

>>>>

$$ ext_1 = \phi_1 TAI_l $$
$$ ext_2 = \phi_2 TAI_l $$
$$ \tau_{diff} = (1 - CAI) - CAI exp\left( -ext_1 - ext_2 \right) ext_1^2 e^{exp_1} E_i(-exp_1) + (ext_1 - 1)$$

@@

Single-scattering albedo ($w_0$):

$$ w_0 = \frac{1}{2} \frac{a_{proj}}{\phi_2 \mu + a_{proj}} \frac{1 - \phi_1 \mu}{\phi_2 \mu a_{proj}}
  \log \left( 1 + \frac{\phi_2 \mu + a_{proj}}{\phi_1 \mu} \right) $$

Beam backscatter ($\gamma$):

$$ \gamma = w_0 \frac{1 + \bar{\mu} \lambda}{\bar{\mu} \lambda} $$
